---
title: "Stock Price Prediction"
author: "Shailesh Mahto(50540379), Abhiroop(______), Shivam(______), Kshitij(______)"
date: "2024-05-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyquant)

library(tibble)
library(dplyr)
library(tidyr)
library(readr)
library(lubridate)
library(ggplot2)
library(ggfortify)

# tsibble: tidy temporal data frames and tools
library(tsibble)

# fable (forecast table)
library(fable)

# fabletools - provides tools for building modelling packages, with a focus on time series forecasting
library(fabletools)

# Feature Extraction and Statistics for Time Series in tsibble format
library(feasts)
```

```{r}
apple <- tq_get('AAPL', from = '2020-01-01', to = '2024-05-01') 
apple <- apple|>
    select(date, close) |>
    mutate(day = seq.int(nrow(apple))) |>
    select(day, close) |> 
    as_tsibble(
      index = day
    )
autoplot(apple)
```

```{r}
# using all data except last 100 days for training
train_apple <- apple |> filter(day <= 989)
```
## ETS Model
1. Used Box-cox transformation to stabilize variance
2. Created ETS model and reported autoselected model: ETS(A,N,N)
3. Checked residuals visually and using Ljung-Box test to ensure it is indistinguishable from white noise.
4. Forecasred for the next 100 days and reported accuracy.
```{r}
train_apple %>%
  features(close, features = guerrero) 
lambda_guerrero = 1.232205

apple_ets <- train_apple |>
  model(ets = ETS(box_cox(close, lambda_guerrero)))

apple_ets |> report()

components(apple_ets) |> autoplot()

apple_ets |>
  gg_tsresiduals() + 
  labs(title = "Residual Diagnostics for ETS(A, N, N)")

# using lag=min(2m, T/5) for seasonal data and 10 for non-seasonal data
augment(apple_ets) %>%
  features(.innov, ljung_box, lag = 10)

apple_ets_fc <- apple_ets %>%
  forecast(h = 100) 

apple_ets_fc%>%
  autoplot(apple)

apple_ets_fc |> accuracy(apple)

```
## ARIMA Model
1. Used Box Cox transoformation to stabilize the variance
2. Converted the data to stationary for modelling 
3. Created an ARIMA(2,1,4) model.
4. Ensured its residuals are indintinguishable from white noise-visually and using Ljung-Box test.
5. Reported the model's performance.
```{r}
train_apple %>%
  features(close, features = guerrero) 
lambda_guerrero = 1.232205

# transform data for constant variance
train_apple %>% autoplot(box_cox(close, lambda_guerrero)) +
  labs(y = "Box-Cox transformed closing price")

# check for number of seasonal differencing = 0
train_apple %>% features(box_cox(close, lambda_guerrero), unitroot_nsdiffs)

# check for first-order differencing = 1
train_apple |> features(box_cox(close, lambda_guerrero), unitroot_ndiffs)

gg_tsdisplay(train_apple, difference(box_cox(close, lambda_guerrero)), plot_type='partial', lag_max = 90)
# Obs: ACF drops to 0 quickly, so we can say that the data is now stationary

train_apple |>
  features(difference(box_cox(close, lambda_guerrero)), unitroot_kpss)
# Obs: The data is stationary
```


```{r}
arima_fit <- train_apple %>%
  model(
    arima_auto = ARIMA(box_cox(close, lambda_guerrero), stepwise = FALSE),
    # arima_auto = ARIMA(box_cox(sale, lambda_guerrero), stepwise = False, approx = False)
  )

arima_fit |> pivot_longer(everything(), names_to = "Model name",
                     values_to = "Orders")
```
Autoselected model : ARIMA(2,1,4)
```{r}
glance(arima_fit)

arima_fit |> select(arima_auto) |> gg_tsresiduals(lag=36)

augment(arima_fit) |>
  filter(.model == "arima_auto") |>
  features(.innov, ljung_box, lag=24, dof=6)
```
Observation: The residuals look like white noise, so the model is good. Hence its ready for forecasting.
```{r}
forecast(arima_fit, h=100) |>
  filter(.model=='arima_auto') |>
  autoplot(apple) +
  labs(title = "Closing price actual and forecast using ARIMA(2,1,4)",
       )

forecast(arima_fit, h=100) |>
  filter(.model=='arima_auto') |> 
  accuracy(apple)

```


## Comparing models
We observe that ARIMA model performs better than the ETS model but their performance is close. 
```{r}
train_apple |>
   model(
   arima = ARIMA(box_cox(close, lambda_guerrero) ~ pdq(2,1,4)),
   ets = ETS(box_cox(close, lambda_guerrero) ~ error("A") + trend("N") + season("N"))
   ) |>
   forecast(h = 100) |>
   accuracy(apple) 
```

````{r}

````

````{r}

````

````{r}

````

````{r}

````
